Final Project Data 205

### 2021-12-05 Draft Final Project1.Rmd
Add files via upload

```{r}
WKridership<- read_csv("2019 Ridership weekday average.csv")
crimes<-read_csv("crime.csv")
``` 
# Examine the data
```{r}
str(WKridership)
head(WKridership)
```
## create dataframe from CSV
```{r}
year<- c("2010","2011","2012","2013","2014","2015","2016","2017","2018","2019","2020","2021")
averider<- c(705563,737313,721225,706591,693705,675077,621079,613665,605910,626269,176602,125557)
dailyentriesride<-data.frame(year,averider)
print(dailyentriesride)
```
# Barplot Average Daily Entries 
```{r}
options(scipen = 999)
ggplot(data=dailyentriesride, aes(x=year, y=averider)) +
  geom_bar(stat="identity", fill="red")+
  geom_text(aes(label=averider), vjust=1.6, color="white", size=3.5)+
   xlab("Year") +
  ylab("Passengers") +
  ggtitle("Average Daily Entries By Train") +
  ylim(0,800000)
  theme_minimal()
```
##Barplot Average Daily Entries by Bus

```{r}
year<- c("2010","2011","2012","2013","2014","2015","2016","2017","2018","2019","2020","2021")
averider<- c(705563,737313,721225,706591,693705,675077,621079,613665,605910,626269,176602,125557)
dailyentriesride<-data.frame(year,averider)
print(dailyentriesride)
```

@@

url <- "https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-"
time_periods <- c("October-2021","September-2021", "August-2021", "July-2021", "June-2021","May-2021","April-2021","March-2021","February-2021","January-2021","December-2020","November-2020","October-2020","September-2020", "August-2020")

url <-"https://www.wmata.com/about/transit-police/upload/June-2020-Blotter-Report"

@@

  if (df_prev == "")
  {
    df_prev <- df_curr
    df_wmata <- df_prev
  } else {
    df_wmata <- bind_rows(df_wmata, df_curr)
  }
}

@@

>>>>

```{r}
WKridership<- read_csv("2019 Ridership weekday average.csv")
crimes<-read_csv("crime.csv")
``` 
# Examine the data
```{r}
str(WKridership)
head(WKridership)
```
## create dataframe from CSV
```{r}
year<- c("2010","2011","2012","2013","2014","2015","2016","2017","2018","2019","2020","2021")
averider<- c(705563,737313,721225,706591,693705,675077,621079,613665,605910,626269,176602,125557)
dailyentriesride<-data.frame(year,averider)
print(dailyentriesride)
```
# Barplot Average Daily Entries 
```{r}
options(scipen = 999)
ggplot(data=dailyentriesride, aes(x=year, y=averider)) +
  geom_bar(stat="identity", fill="red")+
  geom_text(aes(label=averider), vjust=1.6, color="white", size=3.5)+
   xlab("Year") +
  ylab("Passengers") +
  ggtitle("Average Daily Entries By Train") +
  ylim(0,800000)
  theme_minimal()
```

@@

url <- "https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-"
time_periods <- c("October-2021","September-2021", "August-2021", "July-2021", "June-2021","May-2021","April-2021","March-2021","February-2021","January-2021","December-2020","November-2020","October-2020","September-2020","August-2020","May-2020","April-2020","March-2020","February-2020","January-2020","December-2019","November-2019","October-2019","June-2019","November-2018")

url_exception_june_2020<-"https://www.wmata.com/about/transit-police/upload/June-2020-Blotter-Report.pdf"
df_exception_June_2020 <- get_wmata_data(url_exception_june_2020)

url_exception_july_2020<-"https://www.wmata.com/about/transit-police/upload/July-2020-Blotter.pdf"
df_exception_July_2020 <- get_wmata_data(url_exception_july_2020)

url_exception_july_2019<-"https://www.wmata.com/about/transit-police/upload/July-2019-Blotter.pdf"
df_exception_July_2019 <- get_wmata_data(url_exception_July_2019)

url_exception_may_2019<-"https://www.wmata.com/about/transit-police/upload/May-2019-Blotter-Report.pdf"
df_exception_May_2019 <- get_wmata_data(url_exception_May_2019)

url_exception_april_2019<-"https://www.wmata.com/about/transit-police/upload/Blotter-Report-April-2019.pdf"
df_exception_April_2019 <- get_wmata_data(url_exception_April_2019)

url_exception_march_2019<-"https://www.wmata.com/about/transit-police/upload/2019-March-Blotter-Report.pdf"
df_exception_March_2019 <- get_wmata_data(url_exception_March_2019)

url_exception_february_2019<-"https://www.wmata.com/about/transit-police/upload/February-2019-Monthly-Blotter-Report.pdf"
df_exception_February_2019 <- get_wmata_data(url_exception_February_2019)

url_exception_january_2019<-"https://www.wmata.com/about/transit-police/upload/January-2019-Monthly-Blotter-Report.pdf"
df_exception_January_2019 <- get_wmata_data(url_exception_January_2019)

url_exception_december_2018<-"https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-2018-December.pdf"
df_exception_December_2018 <- get_wmata_data(url_exception_December_2018)

url_exception_october_2018<-"https://www.wmata.com/about/transit-police/upload/October-2018-Monthly-Crime-Blotter.pdf"
df_exception_October_2018 <- get_wmata_data(url_exception_October_2018)

url_exception_september_2018<-"https://www.wmata.com/about/transit-police/upload/September-2018-Blotter.pdf"
df_exception_September_2018 <- get_wmata_data(url_exception_September_2018)

url_exception_august_2018<-"https://www.wmata.com/about/transit-police/upload/August-2018-Monthly-Blotter.pdf"
df_exception_August_2018 <- get_wmata_data(url_exception_August_2018)

@@

  if (df_prev == "")
  {
    df_prev <- df_curr
    df_wmata <- df_prev
  } else {
    df_wmata <- bind_rows(df_wmata, df_curr,url_exception_june_2020,url_exception_june_2020,url_exception_march_2019,url_exception_february_2019,url_exception_january_2019,url_exception_december_2018,url_exception_october_2018,url_exception_september_2018,url_exception_august_2018)
  }
}

@@

```{r}
